%-------------------------
% Resume in Latex
% Author : Ches Davidson
% Based off of: https://github.com/cld0033/Resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[8]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
      \textit{\small#7} & \textit{\small #8} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeJobheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Chester Davidson} \\ \vspace{1pt}
    \small 423-364-1544 $|$ \href{mailto:x@x.com}{\underline{cld0033@auburn.edu}} $|$ 
    \href{https://linkedin.com/in/chesterdavidson}{\underline{linkedin.com/in/chesterdavidson}} $|$
     \href{https://github.com/cld0033}{\underline{github.com/cld0033}}
\end{center}

\section{Objective}
    \begin{center}Results-driven professional currently pursuing a degree in Computer Science. Leveraging my previous management and leadership experience to find a Software Engineering Internship.\end{center}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Auburn University}{Auburn, Al}
      {Bachelor of Science in Computer Science}{Jan. 2024 -- Dec. 2025}
      {Masters of Science in Exercise Physiology}{Aug. 2017 -- Aug. 2018}
      {Bachelor of Science in Kinesiology}{Aug. 2013 -- May 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    
    \resumeJobheading
    {Forever Florida Real Estate}{St. Petersburg, Fl}
    {Realtor}{Mar. 2023 -- Present}
    \resumeItemListStart
        \resumeItem{Advised clients on market trends, property values, and investment opportunities, enabling them to make informed decisions and achieve their real estate goals.}
        \resumeItem{Utilized effective negotiation skills to secure favorable terms and agreements for clients, maximizing their financial outcomes.}
        \resumeItem{Developed and executed comprehensive marketing strategies for properties, including professional photography, virtual tours, and targeted online and offline campaigns.}
        \resumeItem{Consistently met and exceeded sales targets, earning recognition as a top performer within the company.}
    \resumeItemListEnd
    \resumeJobheading
    {Cherokee Town and Country Club}{Atlanta, Ga}
    {Swim and Fitness Operations Manager}{Sept. 2019 -- Mar. 2023}
    \resumeItemListStart
        \resumeItem{Managed overall operations of fitness centers, pools, and member locker rooms}
        \resumeItem{Led multiple successful capital projects and renovations, enhancing facility appeal and functionality.}
        \resumeItem{Tracked employee time-cards and maintained payroll data accuracy.}
        \resumeItem{Supervised and efficiently scheduled a team of 20+ employees, ensuring their productivity and safety.}
        \resumeItem{Conducted interviews, made hiring decisions, and provided comprehensive training to new and existing staff.}
        \resumeItem{Oversaw procurement and inventory management for essential facility operation}
    \resumeItemListEnd
        
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Title}{Dates}
%     \resumeItemListStart
%        \resumeItem{}
%          {}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

   
%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
        {\textbf {Spherocylinder Calculator} $|$ Java, JUnit}{March 2024}
        \resumeItemListStart
            \resumeItem{Created classes to define an Spherocylinder and an array of Spherocylinder}
            \resumeItem{Defined methods to be able to calculate total and average Surface Area's and Volumes of each element in array}
            \resumeItem{Programmed Test cases using the JUnit framework to achieve conditional coverage}
        \resumeItemListEnd
        \resumeProjectHeading
        {\textbf {Cloud Data Cost} $|$ Java, JUnit}{April 2024}
        \resumeItemListStart
            \resumeItem{Developed classes to represent different types of data}
            \resumeItem{Programmed a Scanner to read in data points and calculate the current cost of data coverage}
            \resumeItem{Implemented JUnit to test the methods ensuring functionality across all classes}
        \resumeItemListEnd
        \resumeProjectHeading
        {\textbf{Rock, Paper, Scissors} $|$ HTML/CSS, JavaScript}{May 2024}
        \resumeItemListStart
            \resumeItem{Developed a mini game of Rock, Paper, Scissors to be played in the browser}
            \resumeItem{Used JavaScript to program the interface of the game and CSS to style the page}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, HTML/CSS, JavaScript (learning)} \\
     \textbf{Libraries}{: React (learning)} \\
     \textbf{Frameworks}{: JUnit} \\
     \textbf{Developer Tools}{: Git, IntelliJ, VS Code} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}


%-------------------------------------------
\end{document}
